\chapter{Acknowledgements}

\section*{Kickstarter Project}
We launched a Kickstarter project to build a test network of Lumos DC boards for final testing
and debugging before releasing the final designs and firmware as an open source \acronym{DIY}
project.

Thank you to all our Kickstarter backers who made the final testing of the Lumos DC controllers
possible!

\begin{center}
\begin{tabular}{ll}
\multicolumn{2}{c}{\bfseries Fan Level}\\
Amanda Allen\\
\multicolumn{2}{c}{{\huge\strut}\bfseries Supporter Level}\\
Carey Adams &
Beth Gordon  \\
Sue Allen &
Sara Jacobson \\
Andrej \v Cibej &
Tanya Spackman \\
Betsy Fernley \\
\multicolumn{2}{c}{{\huge\strut}\bfseries Backer Level}\\
DC \\
\multicolumn{2}{c}{{\huge\strut}\bfseries Silver Level}\\
David Johnston & Melf \\
\multicolumn{2}{c}{{\huge\strut}\bfseries Gold Level}\\
Rob Beasley & Phil Willoughby \\
\multicolumn{2}{c}{{\huge\strut}\bfseries Patron Level}\\
%Casey Annis&
Casey A.&
Robert A. Nesius\\
William H. Ayers&
Patrick Quinn-Graham\\
Jon and Rebecca Garver&
Jama Scaggs\\
Andy Kitzke&
Doug Van Camp\\
Joseph Moss&
Matthew Wentworth
\end{tabular}
\end{center}
We also wish to thank Darren Bliss who has been a great supporter of the Lumos project
since the very first prototype was being experimented with, and the other Kickstarter 
backers and friends who offered moral support, 
other contributions, or who wished to contribute anonymously.
\section*{Technical Legacy}\label{sec:legacy}
The do-it-yourself computerized Christmas light hobby thrives as a community of enthusiasts
who contribute their ideas and designs for others to build, enjoy, and improve upon with new
designs of their own.  
This journey began for me years ago with the discovery of Hill Robertson's Computer Christmas
website ({\ttfamily www.computerchristmas.com}).  It continues on many other sites including 
Chuck Smith's Planet Christmas ({\ttfamily www.planetchrist\-mas\-.com}), 
{\ttfamily doityourselfchristmas.com}, and many others.  

Over the years the users of these forums have produced some great designs which have become
\emph{de facto} standards as others adopt them and refine them in their own designs.  The Lumos
boards' \mc{TRIAC} and \mc{MOSFET} relay circuits (the final few components at the controlled
outputs) are a continuation of the standard circuits used by those communities, inspired most
by Robert Stark's \mc{TRIAC} design and the \mc{DC} \mc{MOSFET} circuits by John Wilson (from Computer
Christmas and Do It Yourself Christmas, respectively).  I am pleased to contribute my own
innovations on these common design themes back to the same community (the remainder of the
Lumos circuits other than the \acronym{TRIAC} and \acronym{MOSFET} output sections are entirely
my own original design).
